Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-28 cbm-rbd-paper.tex
very early failures tauhist figure (section 6)

\section{Numerical examples for a complex system}
\label{sec:examples}

@@

Here, we illustrate our procedure under three different exemplary failure time histories.
(A systematic simulation study is then presented in Section~\ref{sec:sim}.)

@@

The third failure history contains very late failures for all component types
by assuming $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$,
and following the system until $\tnow = 14$.
The late failure times for type $C$ components are especially surprising,
with the prior predictive reliability being $0.01$ at time $10$
(see top left panel of Figure~\ref{fig:compprior1fig1}).
Here, the situation is more extreme than in the first failure history.
Figure~\ref{fig:tauhist3fig3} shows that, after a first short dip,
$\tausnow$ for the continuous update model steadily increases until the first observed failure at $\tnow = 8$.
For the model without update, $\tausnow$ steadily decreases instead,
ignoring any information on component behaviour to be gained during the current system run.
Assuming $\tthresh = 0.5$, the method without parameter update would recommend to maintain the system preventively at $\tnow = 8.4$,
with only $P_2$ having failed by then, and all other components up and running,
corresponding to a considerable waste of component lifetime.

\begin{figure}
\includegraphics[width=\textwidth]{tauhist3fig3}
\caption{Effect of the continuous parameter update for the third failure history,
containing very late failures for all component types ($C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$).}
\label{fig:tauhist3fig3}
\end{figure}

>>>>

\section{Further elaboration of the case study}
\label{sec:examples}

@@

Here, we illustrate our procedure under three different exemplary failure time histories.
(A more systematic simulation study is then presented in Section~\ref{sec:sim}.)

@@

%The third failure history contains very late failures for all component types
%by assuming $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$,
%and following the system until $\tnow = 14$.
%The late failure times for type $C$ components are especially surprising,
%with the prior predictive reliability being $0.01$ at time $10$
%(see top left panel of Figure~\ref{fig:compprior1fig1}).
%Here, the situation is more extreme than in the first failure history.
%Figure~\ref{fig:tauhist3fig3} shows that, after a first short dip,
%$\tausnow$ for the continuous update model steadily increases until the first observed failure at $\tnow = 8$.
%For the model without update, $\tausnow$ steadily decreases instead,
%ignoring any information on component behaviour to be gained during the current system run.
%Assuming $\tthresh = 0.5$, the method without parameter update would recommend to maintain the system preventively at $\tnow = 8.4$,
%with only $P_2$ having failed by then, and all other components up and running,
%corresponding to a considerable waste of component lifetime.
%
%\begin{figure}
%\includegraphics[width=\textwidth]{tauhist3fig3}
%\caption{Effect of the continuous parameter update for the third failure history,
%containing very late failures for all component types ($C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$).}
%\label{fig:tauhist3fig3}
%\end{figure}

The third failure history contains very early failures
with $C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$,
and we follow the system until $\tnow = 0.5$.

***without update consistently higher, adaptive algorithm takes surprisingly early failures into account,
unlike in other scenarios, overall trend for $\tausnow$ constant because of heavy drops,
costs are underestimated without update***

\begin{figure}
\includegraphics[width=\textwidth]{tauhist4fig3}
\caption{Effect of the continuous parameter update for the third failure history,
containing very early failures ($C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$).}
\label{fig:tauhist4fig3}
\end{figure}
